SU($n$) spin models near the Heisenberg critical point

### 2020-04-03 collective_sun/sun_perturbation.tex
add text to introduction

SU($n$) symmetries play an important role in contemporary physics.
Underpinning much of high energy physics, the celebrated SU($n$) gauge
theory known as Yang-Mills theory is central to our understanding of
the electroweak and strong forces.  Extensions of Yang-Mills and
SU($n$) symmetry feature in the most well-studied examples of
holographic duality\cite{maldacena1999largen} and the connection
between entanglement and gravity\cite{ryu2006holographic} through the
anti-de Sitter / conformal field theory (AdS/CFT) correspondence.  In
a condensed matter setting, SU(2) appears ubiquitously as a symmetry
of the Hubbard model, with important consequences for the study of
quantum magnetism and high temperature
superconductivity\cite{lee2006doping}.  The extension of SU(2) spin
models to the case of SU($n$) has led to predictions of exotic new
phases of matter\cite{hermele2009mott, hermele2011topological,
  chen2016syntheticgaugefield, nataf2016chiral}, as well as the
potential to perform universal topological quantum
computation\cite{freedman2004class, nayak2008nonabelian}.
Furthermore, the introduction of disorder into SU($n$) spin models has
opened avenues for studying quantum chaos and information
scrambling\cite{sachdev1993gapless, bentsen2019integrable}.

Last but not least, SU($n$) symmetries appear naturally in the physics
of atomic, molecular, and optical (AMO)
systems\cite{beverland2016realizing, cazalilla2014ultracold,
  gorshkov2010twoorbital, scazza2014observation, taie2012su,
  zhang2014spectroscopic, goban2018emergence, perlin2019effective},
enabling their experimental study with an exquisite level of control.
These symmetries typically appear through the independence of
inter-atomic interaction parameters on the $n$ nuclear spin states of
the individual atoms involved, with e.g.~$n=10$ in the case of
${}^{87}$Sr.

@@

>>>>

SU($n$) symmetries play an important role in contemporary physics.
Underpinning much of high energy physics, the celebrated SU($n$) gauge
theory known as Yang-Mills theory is central to our understanding of
the electroweak and strong forces.  Extensions of Yang-Mills and
SU($n$) symmetry feature in the most well-studied examples of
holographic duality\cite{maldacena1999largen} and the connection
between entanglement and gravity\cite{ryu2006holographic} through the
anti-de Sitter / conformal field theory (AdS/CFT) correspondence.  In
a condensed matter setting, SU(2) appears ubiquitously as a symmetry
of the Hubbard model, with important consequences for the study of
quantum magnetism and high temperature
superconductivity\cite{lee2006doping}.  The extension of the SU(2)
Hubbard model to SU($n$) has led to predictions of exotic phases of
matter such as chiral spin liquids\cite{hermele2009mott,
  hermele2011topological, chen2016syntheticgaugefield,
  nataf2016chiral}, as well as the potential to perform universal
topological quantum computation\cite{freedman2004class,
  nayak2008nonabelian}.  Furthermore, the consideration of disordered
SU($n$) spin models has opened analytically tractable avenues for
studying quantum chaos and information
scrambling\cite{sachdev1993gapless, bentsen2019integrable}.

Last but not least, SU($n$) symmetries appear naturally in the physics
of atomic, molecular, and optical (AMO)
systems\cite{gorshkov2010twoorbital, beverland2016realizing,
  cazalilla2014ultracold, taie2012su, hofrichter2016direct,
  cappellini2014direct, scazza2014observation, zhang2014spectroscopic,
  goban2018emergence, perlin2019effective} through the independence of
atomic orbital and interaction parameters on the $n$ nuclear spin
states of individual atoms, with e.g.~$n=10$ in the case of
${}^{87}$Sr.  As a result, experiments can directly probe the SU($n$)
Hubbard model, leading to experimental observations of SU($n$) Hubbard
phases and phase transitions\cite{taie2012su, hofrichter2016direct},
two-orbital SU($n$) magnetism\cite{cappellini2014direct,
  scazza2014observation, zhang2014spectroscopic}, and multi-body
SU($n$)-symmetric interactions\cite{goban2018emergence,
  perlin2019effective}.  The tremendous theoretical significance of
SU($n$) symmetries makes it all the more exciting that they appear in
experimental platforms with exquisite degrees of microscopic control,
thereby enabling the detailed study of these symmetries' consequences
for fundamental questions in physics, as well as their use in
practical technological applications.  SU(2)-symmetric interactions,
for example, can play an important role in the development of quantum
sensors that make use of entanglement to surpass classical limits on
measurement precision\cite{he2019engineering}\red{[cite XXZ squeezing
  paper]}.  The exciting prospect of similarly exploiting larger
SU($n$) symmetries to achieve a technological advantage is still an
unexplored avenue with enormous potential.

@@

\vfill
